Capstone Movielens Report

### 2025-10-24 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions (Details section): get_log3, get_log4.

This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.get_log3.args.msg_template), [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), and [arg3](#func.get_log3.args.arg3)  arguments, respectively.

@@

This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.get_log4.args.msg_template), [arg1](#func.get_log4.args.arg1), [arg2](#func.get_log4.args.arg2), [arg3](#func.get_log4.args.arg3), and [arg4](#func.get_log4.args.arg4) arguments, respectively.

>>>>

This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to form a character vector from the template passed in the [msg_template](#func.get_log3.args.msg_template) argument, using the values specified by the [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), and [arg3](#func.get_log3.args.arg3)  arguments to replace all the occurrences of the placeholders `%1`, `%2`, and `%3`, respectively, found in the template.

@@

This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to form a character vector from the template passed in the [msg_template](#func.get_log3.args.msg_template) argument, using the values specified by the [arg1](#func.get_log3.args.arg1), [arg2](#func.get_log3.args.arg2), [arg3](#func.get_log3.args.arg3), and [arg4](#func.get_log3.args.arg4) arguments to replace all the occurrences of the placeholders `%1`, `%2`, `%3`, and `%4`, respectively, found in the template.
